The Effectiveness of Strategies to Contain SARS-CoV-2: Testing, Vaccinations, and NPIs

### 2022-03-09 src/rev1_reply_comments.tex
Allow compilation.

          \response{%
              We now cite our main reference for the susceptibilities for each age group also in the main text. We directly take the susceptibilities given by Davies et al. 2020, in their Extended Data Fig. 4.
              We base our assumption on infectiousness being independent of age on Jones et al. 2021. They report only slight differences in viral loads between German adults and children: ``The least infectious youngest children have 78\% (61, 94) of the peak culture probability of adults aged 45 to 55''. Furthermore, they caution that these lower numbers may be due to different sample taking - such as the usage of smaller pediatric swab devices - rather than actual lower viral loads and conclude that the differences, if existent, are likely not clinically relevant.
          }
    \item It is not accurate that the vaccines stop transmission. This has to be adapted accordingly. Also, the authors should state which vaccines they based this analysis on, as in which ones were in use in Germany at that time and how does that affect the relative transmissibility as it cannot be assumed that all vaccines will have the same effect.
          \response{%
          We agree that vaccines do not stop transmission completely. We simplify the way vaccines reduce transmission risk considerably by assuming that 75\% of individuals achieve sterile immunity through a vaccination while the remaining 25\% remain fully susceptible. We are comfortable with this assumption for several reasons: 
          Firstly, the existing evidence supports the assumption that all four vaccines approved in the EU (Biontech/Pfizer, Moderna, AstraZeneca and Johnson&Johnson) provide similar levels of protection in the first few months after vaccination and against the Alpha variant (for details see the last third of appendix A.1), which is the only time period and variant our simulations cover.
          Secondly, given the surprisingly good performance of rapid tests we tried to err on the side of being too optimistic with our modelling of vaccine performance. This is  why we chose the perfect protection from vaccination for a large part of the population. 
          Thirdly, reinfections are not a big issue for the time period that we look at. The incidences were small and the chance of more than one exposure to Covid are negligibly small. Thus, the value added by a probabilistic model of vaccination protection is very small for the period that we cover.
          }
\end{enumerate}
}

>>>>

          \response{%
              We now cite our main reference for the susceptibilities for each age group also in the main text. We directly take the susceptibilities given by Davies et al. 2020, in their Extended Data Fig. 4.
              We base our assumption on infectiousness being independent of age on Jones et al. 2021. They report only slight differences in viral loads between German adults and children: ``The least infectious youngest children have 78\% (61, 94) of the peak culture probability of adults aged 45 to 55''. Furthermore, they caution that these lower numbers may be due to different sample taking - such as the usage of smaller pediatric swab devices - rather than actual lower viral loads and conclude that the differences, if existent, are likely not clinically relevant.
          }
    \item It is not accurate that the vaccines stop transmission. This has to be adapted accordingly. Also, the authors should state which vaccines they based this analysis on, as in which ones were in use in Germany at that time and how does that affect the relative transmissibility as it cannot be assumed that all vaccines will have the same effect.
          \response{%
              We agree that vaccines do not stop transmission completely. We simplify the way vaccines reduce transmission risk considerably by assuming that 75\% of individuals achieve sterile immunity through a vaccination while the remaining 25\% remain fully susceptible. We are comfortable with this assumption for several reasons:
              Firstly, the existing evidence supports the assumption that all four vaccines approved in the EU (Biontech/Pfizer, Moderna, AstraZeneca and Johnson \& Johnson) provide similar levels of protection in the first few months after vaccination and against the Alpha variant (for details see the last third of appendix A.1), which is the only time period and variant our simulations cover.
              Secondly, given the surprisingly good performance of rapid tests we tried to err on the side of being too optimistic with our modelling of vaccine performance. This is  why we chose the perfect protection from vaccination for a large part of the population.
              Thirdly, reinfections are not a big issue for the time period that we look at. The incidences were small and the chance of more than one exposure to Covid are negligibly small. Thus, the value added by a probabilistic model of vaccination protection is very small for the period that we cover.
          }
\end{enumerate}
}
